---
title: "Building Bicycle Maps"
author: "Johannes Wagner"
date: "`r Sys.Date()`"
---

```{r, warning = FALSE, messages = FALSE}
library(tidyverse)
library(sf)
library(tidygeocoder)
library(osrm)
library(maptiles)
library(ggrepel)
library(glue)
library(rlang)
library(scales)
library(patchwork)
library(tidyterra)
library(ggspatial)
library(httr)
```

## Loading the data

At this point the package expects a shapefile for administrative boundaries. This data can be found
with local or national authorities or on specialized websites like https://www.diva-gis.org/.

The Shapefile has to be stored under `data/`in the project directory and needs to contain a column with
a geometry, the administrative level of interest (for example districts) and a unique identifier for the 
administrative units of interest.

Addiotionally the CRS of the final map needs to be specified. The default value is WGS84.

```{r}
load_spatial_data <- function(name = "VG250_KRS", column = "SN_L", filter_by = c("14", "15", "16"), crs = 25832) {

  dir <- getwd()
  dir <- glue("{dir}/data/{name}.shp")

  column <- ensym(column)

  municipalities <- st_read(dir)

  municipalities_tb <- as_tibble(municipalities) %>%
    select(!!column, geometry) %>%
    filter(!!column %in% filter_by)  
  
  municipalities_sf <- st_as_sf(municipalities_tb, crs = crs)

  return(municipalities_sf)
}
```

We write a test to see if the function does what we want:

```{r}

```

## Geocoding a list of locations to visit

The function [] takes a list of locations as input. Please be careful to choose unique identifiers for the
places you want to visit.


The package also provides the option to export the geocoded route as gpx track, which makes it easy to import
into most travel apps.

```{r}
geocode_locations -> function(locations = c("Leipzig", "Lützen", "Weißenfels", "Naumburg", "Bad Kösen", "bad Sulza", "Auerstedt"), crs = 25832, write = FALSE) {

  part_vector <- seq(1, length(locations))

  stops_to_geocode <- tibble(
    part = part_vector,
    location = location_vector
  )

  stops_geocoded <- stops_to_geocode %>%
    geocode(location, method = "osm") %>%
    filter(!is.na(long) & !is.na(lat)) %>%
    st_as_sf(coords = c("long", "lat"), crs = st_crs("EPSG:4326"))

  all_stops_unique <- stops_geocoded %>% 
    slice(1:(n() - 1))

  if (write == TRUE) {
    st_write(obj=all_stops_unique,
         dsn="travelling_route.gpx",
         layer="route",
         driver="GPX",
         delete_dsn=TRUE)
  }

  crs <- st_crs(25832)
  all_stops_unique["geometry"] <- lapply(all_stops_unique["geometry"], st_transform, crs) 


}

```

## Find the best route

We basically adapt the geocoded list of locations and use òsmRoute()` to find the best bicyle route for 
our tour.

```{r}

biketr <- function (route = all_stops_unique) {
  routes_raw <- all_stops_unique %>% 
  rename(
    origin_geometry = geometry,
    origin_location = location
  ) %>% 
  mutate(
    destination_geometry = lead(origin_geometry),
    destination_location = lead(origin_location)
  ) %>% 
  filter(row_number() != n())
}

```

## Formating and Ploting

The main goal is to make a nice visual map with our route and detailed maps for every part of 
the trip using OSM data. This can be done by providing the function `travel_map` with a geolocated
sf object for the route and one as a basemap.

```{r}

fmt_duration <- function(x) {
  # Round to the nearest 15 minutes
  n_seconds <- round(seconds(x * 60) / (15 * 60)) * (15 * 60)
  n_seconds <- seconds_to_period(n_seconds)

  out <- map_chr(n_seconds, \(n) {
    if (seconds(n) <= 59) {
      # If this is less than an hour, don't format anything with hours
      glue("{MM} minutes", MM = minute(n))
    } else {
      extra_day_hours <- day(n) * 24

      glue("{HH} hour{s} {MM} minutes",
        HH = scales::label_comma()(hour(n) + extra_day_hours),
        MM = minute(n),
        s = ifelse(hour(n) == 1, "", "s")
      )
    }
  })

  return(out)
}

fmt_km <- scales::label_number(accuracy = 1, suffix = " km", big.mark = ",")

traveling_map <- function(basemap = municipalities_sf, route = all_stops_unique) {

  total_distance <- sum(routes_geocoded$route_distance) %>% fmt_km()
  total_time <- sum(routes_geocoded$route_duration) %>% fmt_duration()

  municipalities_highlighted <- municipalities_sf %>% 
  mutate(visited = geometry %in% municipalities_sf[all_stops_unique, ]$geometry)

  ggplot() +
    geom_sf(data = municipalities_highlighted, aes(geometry = geometry, fill = visited)) +
    geom_sf(data = routes_geocoded, color = clrs[1]) +
    geom_sf(data = all_stops_unique) +
    geom_label_repel(
      data = routes_geocoded,
      aes(label = paste0(destination_location, " ", distance_text), geometry = destination_geometry),
      stat = "sf_coordinates", seed = 1234,
      size = 3, segment.color = clrs[3], min.segment.length = 0, max.overlaps = 20
    ) +
    annotation_scale(
      location = "bl", bar_cols = c("grey30", "white"),
      unit_category = "metric", text_family = "Overpass"
    ) +
    scale_fill_manual(values = c("grey90", "grey70"), guide = "none") +
    coord_sf(crs = st_crs("EPSG:25832")) + 
    labs(title = glue("{total_distance}; and {total_time} with the bike. Bring it on.")) +
    theme_roadtrip()
}


```