---
title: "Building Bicycle Maps"
author: "Johannes Wagner"
date: "`r Sys.Date()`"
---

```{r, warning = FALSE, messages = FALSE}
library(tidyverse)
library(sf)
library(tidygeocoder)
library(osrm)
library(maptiles)
library(ggrepel)
library(glue)
library(rlang)
library(scales)
library(patchwork)
library(tidyterra)
library(ggspatial)
library(httr)
```

## Loading the data

At this point the package expects a shapefile for administrative boundaries. This data can be found
with local or national authorities or on specialized websites like https://www.diva-gis.org/.

The Shapefile has to be stored under `data/`in the project directory and needs to contain a column with
a geometry, the administrative level of interest (for example districts) and a unique identifier for the 
administrative units of interest.

Addiotionally the CRS of the final map needs to be specified. The default value is WGS84.

```{r}
load_spatial_data <- function(name = "VG250_KRS", column = "SN_L", filter_by = c("14", "15", "16"), crs = 25832) {

  dir <- getwd()
  dir <- glue("{dir}/data/{name}.shp")

  column <- ensym(column)

  municipalities <- st_read(dir)

  municipalities_tb <- as_tibble(municipalities) %>%
    select(!!column, geometry) %>%
    filter(!!column %in% filter_by)  
  
  municipalities_sf <- st_as_sf(municipalities_tb, crs = crs)

  return(municipalities_sf)
}
```

We write a test to see if the function does what we want:

```{r}

```

## Providing a list of locations to visited

The function [] takes a list of locations as input. Please be careful to choose unique identifiers for the
places you want to visit.

```{r}

```


## Geocoding

```{r}

```

## Formating and Ploting

