---
title: "Building Bicycle Maps"
author: "Johannes Wagner"
date: "`r Sys.Date()`"
---

```{r, messages = FALSE}
library(tidyverse)     # ggplot, dplyr, and friends
library(sf)            # Handle spatial data in R in a tidy way
library(tidygeocoder)  # Automated geocoding
library(osrm)          # Access OSRM through R
library(ggrepel)       # Nicer non-overlapping labels
library(glue)          # Easier string interpolation
library(scales)        # Nicer labeling functions
library(patchwork)     # Combine plots nicely
library(ggspatial)     # Nicer map features like scale bars
library(httr)          # HTTP requests
```

This builds on the geocoding tutorial from [Andrew Heiss](https://www.andrewheiss.com/blog/2023/06/01/geocoding-routing-openstreetmap-r/) and extends its 
implementation to use CI and a reproducible approach.

The main idea despite the DevOps technicalities is to train the data gathering aspect of bike maps and build pipelines regarding this task.

Write a function for setting up the theme configuration for the maps.

```{r}
theme_roadtrip <- function() {
  theme_void(base_family = "Overpass Light") +
    theme(
      plot.title = element_text(family = "Overpass", face = "bold", hjust = 0.5),
      strip.text = element_text(
        family = "Overpass ExtraBold", face = "plain",
        size = rel(1.1), hjust = 0.5)
    )
}

# Make labels use Overpass by default
update_geom_defaults("label_repel", 
                     list(family = "Overpass",
                          fontface = "plain"))
update_geom_defaults("label", 
                     list(family = "Overpass",
                          fontface = "plain"))

update_geom_defaults("text_repel", 
                     list(family = "Overpass",
                          fontface = "plain"))
update_geom_defaults("text", 
                     list(family = "Overpass",
                          fontface = "plain"))

# Yellowstone colors
clrs <- NatParksPalettes::natparks.pals("Yellowstone")
```

We also want to define some general format functionality: 

```{r}
fmt_duration <- function(x) {
  # Round to the nearest 15 minutes
  n_seconds <- round(seconds(x * 60) / (15 * 60)) * (15 * 60)
  n_seconds <- seconds_to_period(n_seconds)
  
  out <- map_chr(n_seconds, \(n) {
    if (seconds(n) <= 59) {
      # If this is less than an hour, don't format anything with hours
      glue("{MM} minutes", MM = minute(n))
    } else {
      # I only want to format this as a number of hours. If the duration is
      # longer than 24 hours, seconds_to_period() rolls over into days (i.e.
      # seconds_to_period(60 * 60 * 24) returns "1d 0H 0M 0S"), and it shows
      # zero hours. So we extract the day part of the period, multiply it by 24,
      # and add it to the hour component that we want to display
      extra_day_hours <- day(n) * 24
  
      glue("{HH} hour{s} {MM} minutes",
        HH = scales::label_comma()(hour(n) + extra_day_hours),
        MM = minute(n),
        s = ifelse(hour(n) == 1, "", "s")
      )
    }
  })
  
  return(out)
}

fmt_miles <- scales::label_number(accuracy = 10, suffix = " miles", big.mark = ",")

miles_to_meters <- function(x) {
  x * 1609.344
}

meters_to_miles <- function(x) {
  x / 1609.344
}

km_to_miles <- function(x) {
  meters_to_miles(x * 1000)
}
```

## Community data

This is something that has a multitude of sources depending on the national context. We will start with Germany and then try to extend it to the European context.

In Germany municipality data is provided by the [BKG](https://gdz.bkg.bund.de/index.php/default/digitale-geodaten/verwaltungsgebiete/verwaltungsgebiete-1-250-000-stand-01-01-vg250-01-01.html) and can be downloaded
as shapefile or geopackage. We need to convert them into a `data.frame`or a `tibble`.

```{r}
# Get the ZIP file from BKG
url <- "https://daten.gdz.bkg.bund.de/produkte/vg/vg250_ebenen_0101/aktuell/vg250_01-01.utm32s.shape.ebenen.zip"

response <- GET(url)

if (response$status_code == 200) {
  writeBin(response$content, "../data/shapefile.zip")
} else {
  stop("Could not download zip file")
}

# Unzip the file
unzip(shapefile.zip)

# Download the shapefile
municipalities <- st_read("shapefile.shp")

# Convert the shapefile into a tibble
municipalities_tb <- as_tibble(municipalities)

# # filter the layer of interest
# lower_48 <- us_states %>% 
#   filter(!(NAME %in% c("Alaska", "Hawaii", "Puerto Rico")))
```

In general we want to use the ggplot library to plot our data.

```{r}
ggplot() + 
  geom_sf(data = lower_48) +
  coord_sf(crs = st_crs("EPSG:25832")) +  # UTM 32N
  theme_roadtrip()
```